---
title: "Overview of epidemiar package"
author: "Dawn Nekorchuk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of epidemiar package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction


## Modeling Overview

### Modeling Description

bam/gam

Each geographic unit (group) and week is associated with environmental on the day the week began, up to the user-selected number of days in the past (lag length, _l_), so that each group-week has a _l_-day history of weather data. A distributed lag basis is created with the natural cubic splines function (ns, splines library), including intercept, with knots at 25%, 50%, and 75% of the lag length. The 5 basis functions that result are multiplied by each group's history, so that there are just 5 summary statistics, instead of _l_, for every combination of group, week, and environmental covariate. 

## Event Detection Overview

# Data Requirements

## Epidemiology Data

## Environmental Data

## Environmental Reference / Weekly Climate Data

## Reference Tables
1. Environmental variables
1. Model variables and geographic group clusters
1. Population
1. Shapefiles


# Setting up the Model

## Environmental variables
## Geographic grouping clusters

# Setting up for Event Detection
1. Picking the algorithm
1. Settings .... 

# Running epidemiar


# Creating the Report




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
